\thetitle

### 2022-04-27 paper.tex
lit review to own section

% Language selector
\newif\ifen
\enfalse% Change to false to export Korean

@@

\ifen
\else The full text of this paper is available in English at \url{https://github.com/maxkapur/OptimalApplication}.\fi
\end{abstract}

@@

\ifen 본 논문은 \url{https://github.com/maxkapur/OptimalApplication}에서 전문을 한글로 공유한다. \fi
\end{abstract}
\pagebreak

@@

\ifen
We refer to this problem as the \emph{optimal college application} problem, as follows. Consider an admissions market with $m$ colleges. The $j$th college is named $c_j$. Consider a single prospective student in this market, and let each $t_j$-value indicate the utility she associates with attending $c_j$, where her utility is $t_0$ if she does not attend college. Let $g_j$ denote the application fee for $c_j$ and $H$ the student's total budget to spend on application fees. (Alternatively, the budget constraint may represent the time needed to complete each application, or a legal limit on the number of applications permitted.) Lastly, let $f_j$ denote the student's probability of being admitted to $c_j$ if she applies, so that $Z_j$ equals one if she is admitted and zero if not. It is appropriate to assume that the $Z_j$ are statistically independent as long as $f_j$ are probabilities estimated specifically for this student (as opposed to generic acceptance rates). Then the student's objective is to maximize the expected utility associated with the best school she gets into within this budget. Therefore, her optimal college application strategy is given by the solution $\mathcal{X}$ to the problem above, where $\mathcal{X}$ represents the set of schools to which she applies. (The problem is also conformable to other competitive matching games such as job application.)
\else
다음 해석에 따라 이를 `대학 지원 최적화 문제'라고 부른다. $m$개의 대학교를 가지는 입학 시장을 고려하자. $j$번째 학교의 이름은 $c_j$이다. 어떤 학생이 $c_j$에 입학하게 되면 효용 $t_j$를 얻게 된다고 하자. 단, 어떤 대학에도 진학하지 않는 경우 그 학생의 효용은 $t_0$이다. $c_j$의 지원 비용이 $g_j$이며 학생이 지원에 쓸 수 있는 예산이 $H$라고 하자. (예산 제약 조건은 또한 원서를 작성하는 시간이나 지원 개수에 대한 법적인 제한을 나타낼 수도 있다.) 마지막으로, $c_j$에 지원하면 학생이 합격할 확률이 $f_j$이라고 하자. 따라서 합격하면 $Z_j = 1$, 합격 안 하면 $Z_j = 0$이 된다. $f_j$가 (학교의 전체적인 합격률이 아니라) 바로 이 학생의 합격 확률일 때 $Z_j$의 확률적 독립성은 적절한 가정이다. 그러면 학생의 목표는 주어진 예산 안에서 학생이 합격하는 학교들에서 얻는 효용 중 기대 최댓값을 최대화하는 것이다. 위 문제의 최적해가 $\mathcal{X}$일 때, 학생의 최적 대학 지원 전략은 $\mathcal{X}$에  속한 학교로 지원하는 것이다. (취직 전략과 같은 유사한 경쟁적 매칭 게임에도 위에 문제를 적용할 수 있다.)
\fi

\ifen
The college application problem is not solely of theoretical interest. In the American college consulting industry, students pay private consultants an average of \$200 per hour for assistance in preparing application materials, estimating their admissions odds, and identifying target schools (Sklarow 2018). In Korea, an important revenue stream for admissions consulting firms such as Megastudy (\url{megastudy.net}) and Jinhak (\url{jinhak.com}) is ``mock application'' software that claims to use artificial intelligence to optimize the client's application strategy.  Due to the widespread perception that career earnings depend on college admissions outcomes, the solution of \eqref{headlineproblem} holds monetary value. However, although predicting admissions outcomes on a school-by-school basis is a standard benchmark for regression models (Acharya et al. 2019), we believe our study is the first to formulate the overall application strategy as an optimization problem. 
\else
대학 지원 최적화 문제는 이론적인 화제일 뿐만이 아니다. 미국 입학 컨설팅 산업에서 대학 지원 서류 작성, 합격 확률 추정, 그리고 지원 학교를 선택하는 데에 자문하는 개인 상담가의 시간당 급료는 평균 200달러이다 (Sklarow 2018). 한국에서, 메가스터디(\url{megastudy.net})와 진학(\url{jinhak.com})과 같은 입학 컨설팅 기업의 주된 수입원 중 인공지능을 활용하여 학생의 지원 전략을 최대화한다고 홍보하는 ``모의 지원'' 소프트웨어가 있다. 미래의 소득이 대학 입학 결과로 결정된다는 넓은 인식에 따라, \eqref{headlineproblem}의 최적해는 금전적인 가치를 가지고 있다. 그러나, 학교 개별 합격 확률을 추정하는 것은 회귀 분석 모형의 익숙한 응용 사례(Acharya et al. 2019)이지만, 전체적인 지원 전략을 최적화 문제로 모형화한 것은 본 연구의 새로운 기여로 보인다.
\fi

\ifen
From a methodological standpoint, as Fu (2014) remarked, college application represents a somewhat subtle asset allocation problem. In computational finance, traditional portfolio optimization models weigh the sum of expected profit across all assets against a risk term, yielding a concave maximization problem with linear constraints (Markowitz 1952; Meucci 2005). But college applicants maximize the expected value of their \emph{best} asset: If a student is admitted to her $j$th choice, then she is indifferent as to whether she gets into her $(j+1)$th choice. As a result, the valuation function that students maximize is \emph{convex} in the expected utility associated with individual applications. Risk management is implicit in the college application problem because, in a typical admissions market, college preferability is negatively correlated with competitiveness. That is, students negotiate a tradeoff between attractive, selective “reach schools” and less preferable “safety schools” where admission is a safer bet (Jeon 2015). Finally, the combinatorial nature of the college application problem makes it difficult to solve using the gradient-based techniques used in continuous portfolio optimization. Fu estimated her equilibrium model (which considers application as a \emph{cost} rather than a constraint) by clustering the schools so that $m=8$, a scale at which enumeration is tractable. We pursue a more general solution.
\else
방법론적인 관점에서 보면, Fu (2014)가 주장한 바처럼 대학 지원 전략은 약간 미묘한 자산 배분 문제이다. 재정학 분야에서 고전적 포트폴리오 최적화 모형은 전체 자산에 대한 기대 총이익에서 위험회피 항을 뺌으로 선형식으로 제약된 오목 최대화 문제를 이룬다 (Markowitz 1952; Meucci 2005). 그러나 대학 지원자는 가치가 제일 높은 단일 자산의 기대 가치를 최대화하고자 한다. 어떤 학생이 자신이 $j$번째로 선호하는 학교에 합격하면 $(j+1)$번째 학교의 합격 여부는 무관한 상황이 된다. 이는 학생이 최대화하려는 함수를 각 지원 발송의 기대 효용에 대해 오목이 아닌 볼록 함수로 만든다. 또한 입학 시장에서는 전형적으로 대학의 효용과 합격 확률이 서로 반비례하므로 대학 지원 문제는 위험 관리를 포함하게 된다. 특히 선호도가 높으며 붙기 어려운 “상향” 지원 학교(reach school)와 선호도가 낮으며 붙기 쉬운 “안정” 지원 학교(safety school) 사이의 균형을 고려해야 한다 (전민희 2015). 마지막, 대학 지원의 조합적인 본질로 인해 연속적인 포트폴리오 최적화 문제에서 흔히 사용하는 기울기 해법으로는 풀기가 어렵다. Fu는 지원 비용을 제약 조건 대신 목적함수의 한 항으로 모형화했으며, 균형 모형의 모수를 추정하기 위해 $m=8$이 되도록 학교들의 클러스터를 먼저 구성했다. 이는 열거법을 통해 문 쉽게 풀 수 있는 규모이지만 본 연구는 더 일반적인 $m$에 대한 해법을 추구한다.
\fi

\ifen
The integer formulation of the college application problem can also be viewed as a kind of binary knapsack problem with a polynomial objective function of degree $m$. Our branch-and-bound and dynamic programming algorithms closely resemble existing algorithms for knapsack problems (Martello and Toth 1990, \S\,2.5--6). In fact, by manipulating the admissions probabilities, the objective function can be made to approximate a linear function of the characteristic vector to an arbitrary degree of accuracy, a fact that we exploit in our NP-completeness proof. Previous research has introduced various forms of stochasticity to the knapsack problem, including variants in which each item's utility takes a known probability distribution (Steinberg and Parks 1979; Carraway et al. 1993) and an online context in which the weight of each item is observed after insertion into the knapsack (Dean et al. 2008). Our problem superficially resembles the preference-order knapsack problem considered by Steinberg and Parks and Carraway et al., but these models lack the college application problem's singular ``maximax'' form. Additionally, unlike those models, we do not attempt to replace the real-valued objective function with a preference order over \emph{outcome distributions,} which introduces technical issues concerning competing notions of stochastic dominance (Sniedovich 1980). We take for granted the student's preferences over \emph{outcomes} (as encoded in the $t_j$-values), and focus instead on an efficient computational approach to the well-defined problem above.
\else
대학 지원 문제의 정수 모형은 $m$차 다항식을 목적함수로 갖춘 일종의 이진 배낭 문제로 볼 수도 있다. 본 논문에서 제시하는 분지한계법과 동적 계획 해법은 배낭 문제를 위한 기존 알고리즘과 매우 비슷하다 (Martello와 Toth 1990, \S\,2.5--6). 입학 확률을 적당히 조정하면 특성벡터의 선형 함수를 원래 목적함수로 원하는 만큼의 정확성을 가지고 근사할 수 있으며 NP-completeness 증명에서 이 성질을 활용한다. 배낭 문제에 확률성을 도입한 선행 연구 중, 각 상품의 효용이 정해진 확률 분포로 결정되는 모형(Steinberg와 Parks 1979; Carraway 외 1993), 그리고 배낭에 삽입한 다음에 상품의 무게를 관측할 수 있는 온라인 모형 (Dean 외 2008) 등이 있다. 본 연구가 고려하는 문제는 Steinberg와 Parks 그리고 Carraway 외가 고려한 ``우선순위 배낭 문제''와는 유사성을 가지지만, 우선순위 배낭 문제는 대학 지원 문제의 특색인 `maximax' 형태를 가지지는 않는다. 또한 우선순위 모형과 달리, 본 연구에서 실수값 목적함수를 선호 순위를 정의해야 하는 `결과 분포'로 대체할 필요가 없다. 확률적 우위에 대한 상반된 개념들의 문제를 야기시키기 때문이다 (Sniedovich 1980). 대신 $t_j$-값으로 유도된 학생의 `결과'에 대한 선호 순위를 받아들여 위에서 정의한 것처럼 명확히 정의된 문제를 위한 효율적인 계산법을 지향한다.
\fi

@@

\ifen
For certain classes of optimization problems, such as maximizing a submodular set function over a cardinality constraint, a greedy algorithm is known to be a good approximate solution and exact under certain additional assumptions (Fisher et al. 1978). For other problems, notably the binary knapsack problem, the most intuitive greedy algorithm can be made to perform arbitrarily poorly (Vazirani 2001). We show results for the college application problem that mirror those for knapsack: In the special case where each $g_j = 1$, the optimal portfolio satisfy a nestedness property that is equivalent to the validity of the greedy algorithm. This case mirrors the centralized college application process in Korea, where there is no application fee, but students are allowed to apply to only three schools during the main admissions cycle. Unfortunately, the nestedness property does not hold in the general case, nor does the greedy algorithm offer any performance guarantee. Instead, we offer a branch-and-bound routine, a pseudopolynomial-time algorithm that is tractable for typical college market instances, and a fully polynomial-time approximation scheme (FPTAS).
\else
탐욕 알고리즘이 좋은 근사해거나 정확한 알고리즘이 되는 최적화 모형들이 알려져 있다. 집합 크기 제약 하에서 submodular한 집합 함수를 최대화하는 문제가 대표적인 예다 (Fisher 외 1978). 반면에 이진 배낭 문제 같은 경우에서는 가장 직관적인 탐욕 알고리즘이 최적과 거리가 먼 해를 출력하는 예를 만들 수 있다 (Vazirani 2001). 대학 지원 문제와 배낭 문제가 서로 매우 유사함을 보인다. 모든 $g_j=1$인 특수한 경우에서, 최적 포트폴리오가 탐욕 알고리즘의 타당성과 동등한 포함 사슬 관계를 만족하는 것을 증명한다. 이 경우는 지원 비용이 없으며 정시 모집 기간에 학교 3개에만 지원할 수 있는 한국 입학 과정과 같다. 그러나 일반적인 경우에서 포함 사슬 관계가 성립하지 않을뿐더러 탐욕 알고리즘이 어떤 근사 계수를 보장할 수 없을 보일 수 있다. 대신 분지한계법, 전형적인 입학 시장 인스턴스에 대해 효율적인 의사 다항 시간 동적 계획, 그리고 완전 다항 시간 근사 해법(fully polynomial-time approximation scheme, FPTAS)을 제시한다.
\fi

% following sentence buries the lede（
\ifen
Finally, we remark that the objective function of \ref{headlineproblem} is a nondecreasing submodular function. However, our research employs more elementary analytical techniques, and our approximation results are tighter than those associated with generic submodular maximization algorithms. For example, a well-known result of Fisher et al. (1978) implies that the greedy algorithm is asymptotically $(1 - 1/e)$-optimal for the $g_j = 1$ case of the college application problem, whereas we show that the same algorithm is exact. When maximizing a submodular set function over knapsack constraints or matroids, a nearly equivalent approximation ratio is achievable using relaxation techniques (Calinescu et al. 2011; Kulik et al. 2013). But in the general case of the college application problem, the existence of the FPTAS supersedes these results.
\else
마지막으로, \ref{headlineproblem}의 목적함수는 submodular하며 단조 증가하는 함수이다. 그런데, 본 연구는 더 기초적인 분석 기술을 이용하며, 일반적인 submodular 최대화 알고리즘보다 좋은 근사 계수를 얻게 된다. 예를 들어 Fisher 외 (1978)의 잘 알려진 결과에 따라, 대학 지원 문제의 $g_j = 1$인 경우에서 탐욕 해법의 점근적 근사 계수가 $(1 - 1/e)$이 되며, 본 논문에서 같은 해법이 정확함을 보인다. 다중 배낭 제약식 혹은 매트로이드 위에서 submodular 집합 함수를 최대하는 문제에서, 완화 기술을 활용하면 거의 동등한 근사 계수를 이뤄 낼 수 있다 (Calinescu et al. 2011; Kulik et al. 2013). 그러나 일반적인 대학 지원 문제에서, FPTAS의 존재성은 그 결과를 대체한다.
\fi

@@

\ifen
Given an application portfolio, let $p_j(\mathcal{X})$ denote the probability that the student attends $c_j$. This occurs if and only if she \emph{applies} to $c_j$, is \emph{admitted} to $c_j$, and is \emph{rejected} from any school she prefers to $c_j$; that is, any school with higher index. Hence, for $j= 0\dots m$,
\else
주어진 지원 포트폴리오에 대해 학생이 $c_j$로 진학할 확률을 $p_j(\mathcal{X})$라고 하자. 이 사건이 발생하는 필수충분 조건은 $c_j$에 지원하고, $c_j$에서 합격하고, $c_j$보다 선호하는 (즉, 지표가 더 높은) 학교에서 불합격는 것이다. 따라서  $j= 0\dots m$에 대해
\fi
\begin{align}
p_j(\mathcal{X}) &= 
\begin{cases}
\displaystyle f_j  \prod_{\substack{i \in \mathcal{X}: \\ i > j}} (1 - f_{i}), \quad & j \in \{0\}\cup\mathcal{X}\\
0, \quad & \text{\ifen otherwise\else otherwise.\fi}
\end{cases} 
\end{align}
\ifen
where the empty product equals one. The following proposition follows immediately.
\else
단, 공집합의 곱은 1이다. 다음 제의는 직설적인 결과다.
\fi

@@

\subsection{A variable-elimination technique}
\ifen
Now, we present a variable-elimination technique that will prove useful throughout the paper.\footnote{We thank Yim Seho for pointing out this useful transformation.} Suppose that the student has already resolved to apply to $c_k$, and the remainder of her decision consists of determining which \emph{other} schools to apply to. Writing her total application portfolio as $\mathcal{X} = \mathcal{Y} \cup \{k\}$, we devise a function $w(\mathcal{Y})$ that orders portfolios according to how well they ``complement'' the singleton portfolio $\{k\}$. Specifically, the difference between $v(\mathcal{Y} \cup\{k\})$ and $w(\mathcal{Y})$ is the constant $f_k t_k$.
\else
본 항에서 남은 논문에서 활용되는 변수 소거 기술을 소개한다.\footnote{이 유용한 변환을 발견한 임세호에게 감사를 표한다.} 학생이 $c_k$에 지원하기로 결심하고, 남은 결정 공간은 어떤 다른 학교에 지원하는 것으로 제한된다고 하자. 전체 지원 포트폴리오를 $\mathcal{X} = \mathcal{Y} \cup \{k\}$일 때, $\mathcal{Y} \subseteq \mathcal{C} \setminus \{k\}$인 포트폴리오와 $\{k\}$ 사이의 \mbox{`보완성'을} 평가하는 함수 $w(\mathcal{Y})$를 도출할 수 있다. 단, $v(\mathcal{Y} \cup\{k\})$와 $w(\mathcal{Y})$ 사이에서 $f_k t_k$ 같은 상수 차이가 발생한다.
\fi

@@

\ifen \subsection{Properties of the optimal portfolios} \else\subsection{최적 포트폴리오의 성질} \fi
\ifen The nestedness property implies that Alma's expected utility is a discretely concave function of $h$.
\else 포함 사슬 관계 성질은 알마의 기대 효용이 $h$의 이산 오목 함수임을 의미한다.\fi

>>>>

% Language selector
\newif\ifen
\entrue% Change to false to export Korean

@@

\ifen
\else The full text of this paper is available in English at \url{https://github.com/maxkapur/CollegeApplication}.\fi
\end{abstract}

@@

\ifen 본 논문은 \url{https://github.com/maxkapur/CollegeApplication}에서 전문을 한글로 공유한다. \fi
\end{abstract}
\pagebreak

@@

\ifen
We refer to this problem as the \emph{optimal college application} problem, as follows. Consider an admissions market with $m$ colleges. The $j$th college is named $c_j$. Consider a single prospective student in this market, and let each $t_j$-value indicate the utility she associates with attending $c_j$, where her utility is $t_0$ if she does not attend college. Let $g_j$ denote the application fee for $c_j$ and $H$ the student's total budget to spend on application fees. Lastly, let $f_j$ denote the student's probability of being admitted to $c_j$ if she applies, so that $Z_j$ equals one if she is admitted and zero if not. It is appropriate to assume that the $Z_j$ are statistically independent as long as $f_j$ are probabilities estimated specifically for this student (as opposed to generic acceptance rates). Then the student's objective is to maximize the expected utility associated with the best school she gets into within this budget. Therefore, her optimal college application strategy is given by the solution $\mathcal{X}$ to the problem above, where $\mathcal{X}$ represents the set of schools to which she applies. (The problem is also conformable to other competitive matching games such as job application. Here, the budget constraint may represent the time needed to complete each application, or a legal limit on the number of applications permitted.)
\else
다음 해석에 따라 이를 `대학 지원 최적화 문제'라고 부른다. $m$개의 대학교를 가지는 입학 시장을 고려하자. $j$번째 학교의 이름은 $c_j$이다. 어떤 학생이 $c_j$에 입학하게 되면 효용 $t_j$를 얻게 된다고 하자. 단, 어떤 대학에도 진학하지 않는 경우 그 학생의 효용은 $t_0$이다. $c_j$의 지원 비용이 $g_j$이며 학생이 지원에 쓸 수 있는 예산이 $H$라고 하자. 마지막으로, $c_j$에 지원하면 학생이 합격할 확률이 $f_j$이라고 하자. 따라서 합격하면 $Z_j = 1$, 합격 안 하면 $Z_j = 0$이 된다. $f_j$가 (학교의 전체적인 합격률이 아니라) 바로 이 학생의 합격 확률일 때 $Z_j$의 확률적 독립성은 적절한 가정이다. 그러면 학생의 목표는 주어진 예산 안에서 학생이 합격하는 학교들에서 얻는 효용 중 기대 최댓값을 최대화하는 것이다. 위 문제의 최적해가 $\mathcal{X}$일 때, 학생의 최적 대학 지원 전략은 $\mathcal{X}$에  속한 학교로 지원하는 것이다. (취직 전략과 같은 유사한 경쟁적 매칭 게임에도 위에 문제를 적용할 수 있다. 이때, 예산 제약 조건은 원서를 작성하는 시간이나 지원 개수에 대한 법적인 제한을 나타낼 수 있다.)
\fi

\ifen
The college application problem is not solely of theoretical interest. In the American college consulting industry, students pay private consultants an average of \$200 per hour for assistance in preparing application materials, estimating their admissions odds, and identifying target schools (Sklarow 2018). In Korea, an important revenue stream for admissions consulting firms such as Megastudy (\url{megastudy.net}) and Jinhak (\url{jinhak.com}) is ``mock application'' software that claims to use artificial intelligence to optimize the client's application strategy.  Due to the widespread perception that career earnings depend on college admissions outcomes, the solution of \eqref{headlineproblem} holds monetary value. However, although predicting admissions outcomes on a school-by-school basis is a standard benchmark for regression models (Acharya et al. 2019), we believe our study is the first to focus on the overall application strategy as an optimization problem. 
\else
대학 지원 최적화 문제는 이론적인 화제일 뿐만이 아니다. 미국 입학 컨설팅 산업에서 대학 지원 서류 작성, 합격 확률 추정, 그리고 지원 학교를 선택하는 데에 자문하는 개인 상담가의 시간당 급료는 평균 200달러이다 (Sklarow 2018). 한국에서, 메가스터디(\url{megastudy.net})와 진학(\url{jinhak.com})과 같은 입학 컨설팅 기업의 주된 수입원 중 인공지능을 활용하여 학생의 지원 전략을 최대화한다고 홍보하는 ``모의 지원'' 소프트웨어가 있다. 미래의 소득이 대학 입학 결과로 결정된다는 넓은 인식에 따라, \eqref{headlineproblem}의 최적해는 금전적인 가치를 가지고 있다. 그러나, 학교 개별 합격 확률을 추정하는 것은 회귀 분석 모형의 익숙한 응용 사례(Acharya et al. 2019)이지만, 전체적인 지원 전략에 집중하여 최적화 문제로 모형화한 것은 본 연구의 새로운 기여로 보인다.
\fi

\ifen \subsection{Literature review} \else \subsection{문헌 조사} \fi
%\ifen
The college application problem straddles several methodological universes. Its stochastic nature recalls classical asset allocation models from computational finance. However, the knapsack constraint renders the problem NP-complete and necessitates combinatorial solution techniques. We also observe that the objective function is also a submodular set function, although our approximation results suggest that college application is a relatively easy instance of submodular maximization.
%\else
%대학 지원 문제는 몇 개의 방법론적인 우주를 걸친다. 확률적인 문제인 만큼 재정학 분야... % .....
%\fi

% reword this sentence for a better transition
\ifen
% In an equilibrium analysis of the American college market, Fu (2014) remarked that
% (and change below)
From a methodological standpoint, as Fu (2014) remarked, college application represents a somewhat subtle asset allocation problem. In computational finance, traditional portfolio optimization models weigh the sum of expected profit across all assets against a risk term, yielding a concave maximization problem with linear constraints (Markowitz 1952; Meucci 2005). But college applicants maximize the expected value of their \emph{best} asset: If a student is admitted to her $j$th choice, then she is indifferent as to whether she gets into her $(j+1)$th choice. As a result, the valuation function that students maximize is \emph{convex} in the utility associated with individual applications. Risk management is implicit in the college application problem because, in a typical admissions market, college preferability correlates inversely with competitiveness. That is, students negotiate a tradeoff between attractive, selective “reach schools” and less preferable “safety schools” where admission is a safer bet (Jeon 2015). Finally, the combinatorial nature of the college application problem makes it difficult to solve using the gradient-based techniques used in continuous portfolio optimization. Fu estimated her equilibrium model (which considers application as a \emph{cost} rather than a constraint) by clustering the schools so that $m=8$, a scale at which enumeration is tractable. We pursue a more general solution.
\else
방법론적인 관점에서 보면, Fu (2014)가 주장한 바처럼 대학 지원 전략은 약간 미묘한 자산 배분 문제이다. 재정학 분야에서 고전적 포트폴리오 최적화 모형은 전체 자산에 대한 기대 총이익에서 위험회피 항을 뺌으로 선형식으로 제약된 오목 최대화 문제를 이룬다 (Markowitz 1952; Meucci 2005). 그러나 대학 지원자는 가치가 제일 높은 단일 자산의 기대 가치를 최대화하고자 한다. 어떤 학생이 자신이 $j$번째로 선호하는 학교에 합격하면 $(j+1)$번째 학교의 합격 여부는 무관한 상황이 된다. 이는 학생이 최대화하려는 함수를 각 지원 발송의 효용에 대해 오목이 아닌 볼록 함수로 만든다. 또한 입학 시장에서는 전형적으로 대학의 효용과 합격 확률이 서로 반비례하므로 대학 지원 문제는 위험 관리를 포함하게 된다. 특히 선호도가 높으며 붙기 어려운 “상향” 지원 학교(reach school)와 선호도가 낮으며 붙기 쉬운 “안정” 지원 학교(safety school) 사이의 균형을 고려해야 한다 (전민희 2015). 마지막, 대학 지원의 조합적인 본질로 인해 연속적인 포트폴리오 최적화 문제에서 흔히 사용하는 기울기 해법으로는 풀기가 어렵다. Fu는 지원 비용을 제약 조건 대신 목적함수의 한 항으로 모형화했으며, 균형 모형의 모수를 추정하기 위해 $m=8$이 되도록 학교들의 클러스터를 먼저 구성했다. 이는 열거법을 통해 문 쉽게 풀 수 있는 규모이지만 본 연구는 더 일반적인 $m$에 대한 해법을 추구한다.
\fi

\ifen
The integer formulation of the college application problem can be viewed as a kind of binary knapsack problem with a polynomial objective function of degree $m$. Our branch-and-bound and dynamic programming algorithms closely resemble existing algorithms for knapsack problems (Martello and Toth 1990, \S\,2.5--6). In fact, by manipulating the admissions probabilities, the objective function can be made to approximate a linear function of the characteristic vector to an arbitrary degree of accuracy, a fact that we exploit in our NP-completeness proof. Previous research has introduced various forms of stochasticity to the knapsack problem, including variants in which each item's utility takes a known probability distribution (Steinberg and Parks 1979; Carraway et al. 1993) and an online context in which the weight of each item is observed after insertion into the knapsack (Dean et al. 2008). Our problem superficially resembles the preference-order knapsack problem considered by Steinberg and Parks and Carraway et al., but these models lack the college application problem's singular ``maximax'' form. Additionally, unlike those models, we do not attempt to replace the real-valued objective function with a preference order over \emph{outcome distributions,} which introduces technical issues concerning competing notions of stochastic dominance (Sniedovich 1980). We take for granted the student's preferences over \emph{outcomes} (as encoded in the $t_j$-values), and focus instead on an efficient computational approach to the well-defined problem above.
\else
대학 지원 문제의 정수 모형은 $m$차 다항식을 목적함수로 갖춘 일종의 이진 배낭 문제로 볼 수 있다. 본 논문에서 제시하는 분지한계법과 동적 계획 해법은 배낭 문제를 위한 기존 알고리즘과 매우 비슷하다 (Martello와 Toth 1990, \S\,2.5--6). 입학 확률을 적당히 조정하면 특성벡터의 선형 함수를 원래 목적함수로 원하는 만큼의 정확성을 가지고 근사할 수 있으며 NP-completeness 증명에서 이 성질을 활용한다. 배낭 문제에 확률성을 도입한 선행 연구 중, 각 상품의 효용이 정해진 확률 분포로 결정되는 모형(Steinberg와 Parks 1979; Carraway 외 1993), 그리고 배낭에 삽입한 다음에 상품의 무게를 관측할 수 있는 온라인 모형 (Dean 외 2008) 등이 있다. 본 연구가 고려하는 문제는 Steinberg와 Parks 그리고 Carraway 외가 고려한 ``우선순위 배낭 문제''와는 유사성을 가지지만, 우선순위 배낭 문제는 대학 지원 문제의 특색인 `maximax' 형태를 가지지는 않는다. 또한 우선순위 모형과 달리, 본 연구에서 실수값 목적함수를 선호 순위를 정의해야 하는 `결과 분포'로 대체할 필요가 없다. 확률적 우위에 대한 상반된 개념들의 문제를 야기시키기 때문이다 (Sniedovich 1980). 대신 $t_j$-값으로 유도된 학생의 `결과'에 대한 선호 순위를 받아들여 위에서 정의한 것처럼 명확히 정의된 문제를 위한 효율적인 계산법을 지향한다.
\fi

@@

\ifen
For certain classes of optimization problems, such as maximizing a submodular set function over a cardinality constraint, a greedy algorithm is known to be a good approximate solution and exact under certain additional assumptions (Fisher et al. 1978). For other problems, notably the binary knapsack problem, the most intuitive greedy algorithm can be made to perform arbitrarily poorly (Vazirani 2001). We show results for the college application problem that mirror the knapsack problem: When each $g_j = 1$, the optimal portfolios satisfy a nestedness property that is equivalent to the validity of the greedy algorithm. This special case mirrors the centralized college application process in Korea, where there is no application fee, but students are allowed to apply to only three schools during the main admissions cycle. Unfortunately, the nestedness property does not hold in the general case, nor does the greedy algorithm offer any performance guarantee. Instead, we offer a branch-and-bound routine, a pseudopolynomial-time algorithm that is tractable for typical college market instances, and a fully polynomial-time approximation scheme (FPTAS). We also describe a simulated-annealing algorithm that performs well in test instances. 
\else
탐욕 알고리즘이 좋은 근사해거나 정확한 알고리즘이 되는 최적화 모형들이 알려져 있다. 집합 크기 제약 하에서 submodular한 집합 함수를 최대화하는 문제가 대표적인 예다 (Fisher 외 1978). 반면에 이진 배낭 문제 같은 경우에서는 가장 직관적인 탐욕 알고리즘이 최적과 거리가 먼 해를 출력하는 예를 만들 수 있다 (Vazirani 2001). 대학 지원 문제와 배낭 문제가 서로 매우 유사함을 보인다. 모든 $g_j=1$인 특수한 경우에서, 최적 포트폴리오가 탐욕 알고리즘의 타당성과 동등한 포함 사슬 관계를 만족하는 것을 증명한다. 이 경우는 지원 비용이 없으며 정시 모집 기간에 학교 3개에만 지원할 수 있는 한국 입학 과정과 같다. 그러나 일반적인 경우에서 포함 사슬 관계가 성립하지 않을뿐더러 탐욕 알고리즘이 어떤 근사 계수를 보장할 수 없을 보일 수 있다. 대신 분지한계법, 전형적인 입학 시장 인스턴스에 대해 효율적인 의사 다항 시간 동적 계획, 그리고 완전 다항 시간 근사 해법(fully polynomial-time approximation scheme, FPTAS)을 제시한다. 가상 인스턴스에 성능이 좋은 모의 담금질(simulated annealing) 해법도 서술한다. 
\fi

\ifen
Finally, we remark that the objective function of \ref{headlineproblem} is a nondecreasing submodular function. However, our research employs more elementary analytical techniques, and our approximation results are tighter than those associated with generic submodular maximization algorithms. For example, a well-known result of Fisher et al. (1978) implies that the greedy algorithm is asymptotically $(1 - 1/e)$-optimal for the $g_j = 1$ case of the college application problem, whereas we show that the same algorithm is exact. When maximizing a submodular set function over knapsack constraints or matroids, a nearly equivalent approximation ratio is achievable using relaxation techniques (Calinescu et al. 2011; Kulik et al. 2013). But in the general case of the college application problem, the existence of the FPTAS supersedes these results.
\else
마지막으로, \ref{headlineproblem}의 목적함수는 submodular하며 단조 증가하는 함수이다. 그런데, 본 연구는 더 기초적인 분석 기술을 이용하며, 일반적인 submodular 최대화 알고리즘보다 좋은 근사 계수를 얻게 된다. 예를 들어 Fisher 외 (1978)의 잘 알려진 결과에 따라, 대학 지원 문제의 $g_j = 1$인 경우에서 탐욕 해법의 점근적 근사 계수가 $(1 - 1/e)$이 되며, 본 논문에서 같은 해법이 정확함을 보인다. 다중 배낭 제약식 혹은 matroid 위에서 submodular 집합 함수를 최대하는 문제에서, 완화 기술을 활용하면 거의 동등한 근사 계수를 이뤄 낼 수 있다 (Calinescu et al. 2011; Kulik et al. 2013). 그러나 일반적인 대학 지원 문제에서, FPTAS의 존재성은 그 결과를 대체한다.
\fi

@@

\ifen
Given an application portfolio, let $p_j(\mathcal{X})$ denote the probability that the student attends $c_j$. This occurs if and only if she \emph{applies} to $c_j$, is \emph{admitted} to $c_j$, and is \emph{rejected} from any school she prefers to $c_j$; that is, any school with higher index. Hence, for $j= 0\dots m$,
\else
주어진 지원 포트폴리오에 대해 학생이 $c_j$로 진학할 확률을 $p_j(\mathcal{X})$라고 하자. 이 사건이 발생하는 필수충분 조건은 $c_j$에 지원하고, $c_j$에서 합격하고, $c_j$보다 선호하는 (즉, 지표가 더 높은) 학교에서 불합격는 것이다. 따라서  $j= 0\dots m$에 대해
\fi
\begin{align}
p_j(\mathcal{X}) &= 
\begin{cases}
\displaystyle f_j  \prod_{\substack{i \in \mathcal{X}: \\ i > j}} (1 - f_{i}), \quad & j \in \{0\}\cup\mathcal{X}\\
0, \quad & \text{\ifen otherwise\else 그러지 않은 경우.\fi}
\end{cases} 
\end{align}
\ifen
where the empty product equals one. The following proposition follows immediately.
\else
단, 공집합의 곱은 1이다. 다음 제의는 직설적인 결과이다.
\fi

@@

\ifen \subsection{An elimination technique} \else \subsection{변수 소거 기법} \fi
\ifen
Now, we present a variable-elimination technique that will prove useful throughout the paper.\footnote{We thank Yim Seho for pointing out this useful transformation.} Suppose that the student has already resolved to apply to $c_k$, and the remainder of her decision consists of determining which \emph{other} schools to apply to. Writing her total application portfolio as $\mathcal{X} = \mathcal{Y} \cup \{k\}$, we devise a function $w(\mathcal{Y})$ that orders portfolios according to how well they ``complement'' the singleton portfolio $\{k\}$. Specifically, the difference between $v(\mathcal{Y} \cup\{k\})$ and $w(\mathcal{Y})$ is the constant $f_k t_k$.
\else
본 항에서 남은 논문에서 활용되는 변수 소거 기술을 소개한다.\footnote{이 유용한 변환을 발견한 임세호에게 감사한다.} 학생이 $c_k$에 지원하기로 결심하고, 남은 결정 공간은 어떤 다른 학교에 지원하는 것으로 제한된다고 하자. 전체 지원 포트폴리오를 $\mathcal{X} = \mathcal{Y} \cup \{k\}$일 때, $\mathcal{Y} \subseteq \mathcal{C} \setminus \{k\}$인 포트폴리오와 $\{k\}$ 사이의 \mbox{`보완성'을} 평가하는 함수 $w(\mathcal{Y})$를 도출할 수 있다. 단, $v(\mathcal{Y} \cup\{k\})$와 $w(\mathcal{Y})$ 사이에서 $f_k t_k$ 같은 상수 차이가 발생한다.
\fi

@@

\ifen \subsection{Diminishing returns to application} \else\subsection{지원의 수확 체감} \fi
\ifen The nestedness property implies that Alma's expected utility is a discretely concave function of $h$.
\else 포함 사슬 관계 성질은 알마의 기대 효용이 $h$의 이산 오목 함수임을 의미한다.\fi
